Explore the SingleR results

### 2025-07-10 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/explore-singler-results.Rmd
results path

module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
results_dir <- file.path(module_dir, "results", "singler-filtered-genes")
data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
```

>>>>

module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
results_dir <- file.path(module_dir, "results", "singler")
data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
```
